---
title: "HLa001_Study_view_from_window"
author: "Hanneke"
date: "`r Sys.Date()`"
engine: knitr
format: 
  html:
    self-contained: true
    toc: true
    toc_depth: 3
    toc_float: true
    df-print: kable
---

## Template Used

LACDR-ISA - Assay (General) v1.0.0

## Title

`r rmarkdown::metadata$title`

## Date (dd-MM-yyyy)

`r format(Sys.time(), format = "%d-%m-%Y")`

## Description or Purpose

To calculate statistics on what I see outside of my window

### Background

I needed an example for this tutorial and was staring out of my window, so that is what I chose.

### Data sources

A table of objects that I counted. Data stored in data/raw_data/20230502_HLa001_things_I_see_from_my_window.csv

### Analysis plan

1.  Explore the data
2.  Plot the data
3.  Save the results

## Results

### 0. Preparations

#### Load R libraries

```{r}
library(tidyverse)
library(here)
```

#### Set input and output directories

Print where the script was run from:

```{r}
here::here()
```

Set input data directory.

```{r}
data_dir <- here("Tutorial_2_using_LACDR-ISA/data/raw_data")
str_glue("Using data from {data_dir}")
stopifnot(dir.exists(data_dir))
```

Set output data directory and create if it does not exist.

```{r}
datestamp <- str_remove_all(Sys.Date(), "-")
output_dir <- here("Tutorial_2_using_LACDR-ISA/results", str_glue("HLa001_{datestamp}_output"))
if(!dir.exists(output_dir)) dir.create(output_dir)
str_glue("Output directory path is {output_dir}")
```

#### Define functions

```{r}
source(here("Tutorial_2_using_LACDR-ISA/code/functions/example_function.R"))
```

### 1. Load data

```{r}
object_info <- read_csv(here(data_dir, "20230502_HLa001_things_I_see_from_my_window.csv"))
str(object_info)
dim(object_info)
head(object_info)
```

Data looks ok.

### 2. Get information on all cars

```{r}
filter(object_info, object == "car")
```

So I see three car colors, and I think 10 in total, but let's count.

```{r}
object_info %>%
  group_by(object) %>%
  summarise(sum = sum(amount))
```

### 3. Plot the amount of objects

```{r}
p1 <- object_info %>%
  ggplot(aes(x = object, y = amount, fill = color)) +
  geom_col() +
  theme_bw()
p1
```

I clearly see a lot of cars and trees.

#### Save plot

```{r}
ggsave(here(output_dir, "bar_plot_with_info_on_views.png"), p1)
```

### 4. Count to three

To see if I can source and use functions:

```{r}
count_to_three()
# Creating an error here to make sure you cannot reproduce the analysis.
# Delete the line below.
1 + 2 + "three"
```

## Conclusion

Plots were generated and saved. I saw a lot of trees and cars.

### Doubts and limitations

I did not get the colors in the plot the way I want. Redo tomorrow?

### Future assays

Maybe study if I also saw birds.

```{r}
sessionInfo()
```
